Current and future constraints on primordial magnetic fields

### 2016-10-20 pmf.tex
a

>>>>

The sensitivity of CMB experiments is increasing rapidly due to exponentially growing detector counts
\citet{s4sciencebook} thus defines four stages of CMB experiments. 
The current experiments (i.e.~the ones used for PMF constraints in the last section) are classified as Stage II experiments. 
Stage III experiments such as SPT-3G, the Simons Array, or AdvACTPol \citep{spt3g,simonsarray,advactpol} have approximately ten times more detectors, and generically will start collecting data in 2017 and finish in 2020-21.
In this section, we forecast the expected constraints from the Stage III experiments by combining forecasts for SPT-3G and the Simons Array. 
Finally, CMB stage IV is a planned experiment  with another order of magnitude expansion in detector counts that would (ideally) begin taking data in the early 2020s.
We examine the likely PMF constraints from such an experiment, and consider which aspects of experimental or survey design are important to realizing these constraints.

\subsection{Fiducial survey parameters}

\subsection{Stage III forecasts}

\subsection{Stage IV forecasts}

\subsection{Survey considerations for Stage IV}
